---
title: "WTMS - Analysis"
output: 
  html_notebook:
  toc: true
  theme: united
---


# Current Trail Condition

In order to better understand current trail condition, we need to select the records we're interested in.

1) Furniture records which is present

```{r}
Furniture_Present <- filter(Furniture, LatestSurveyCondition != "Not Present")
```

2) Issues which are Unresolved

```{r}

Issues_Unresolved <- filter(Issues, StatusDesc == "Unresolved")

```


## Present Furniture

Start by 


```{r}

AllRecords <- rbind(select(Furniture_Present, RecordType, QS_Group1, QS_Group2), select(Issues_Unresolved, RecordType, QS_Group1, QS_Group2))

AllRecordsTable <- data.frame(table(AllRecords))
```


```{r}

AllRecordsTable <- filter(AllRecordsTable, QS_Group1 %in% c("Boardwalks", "Bridges", "Gates - Other", "Gates Kissing", "Steps - Flights", "Stiles - Ladder", "Stiles - Step", "Stiles - Stone"))



  
```

```{r}
ggplot(data = AllRecordsTable)+
  geom_bar(mapping=aes(x=QS_Group1, y= Freq, fill = RecordType), stat = "Identity", width = 0.7, position = "fill")+
  coord_flip()+
  theme_minimal()+
  scale_fill_manual("RecordType", values = c("Furniture" = "#005eb8", "Issue" = "#ffc72c"))
  
    scale_y_continuous(labels = scales::percent)


```


scale_fill_brewer(type = "qual", palette = "Dark") +


# Trail Condition over time

# Chat with Irina

- some theming packages that sit on top of ggplot
- Knit a markdown file into an output format

## People to ask help from:
- Irina, Henry Knowles (Github), Air Quality teams

Henry tip:
- Write tests
- Unit tests R tools = "Dev tools" + 
- Code looks like "Test_That" 
- Google coding standard - a single function shouldn't be above 40 lines
